CITK - an architecture and examples of CUDA enabled ITK filters

### 2011-05-20 trunk/article/Article.tex
fixed arrows

\subsection{Memory management}
Two base classes have been provided to handle standard filter memory
management - {\em CudaInPlaceImageFilter} and {\em
CudaImageToImageFilter}. These filters allow the standard allocation
structure to be used via {\em this->AllocateOutputs()}. Explicit
allocation of device memory can be achieved using
{\em Image->AllocateGPU()}

>>>>

\subsection{Memory management}
Two base classes have been provided to handle standard filter memory
management - {\em CudaInPlaceImageFilter} and {\em
CudaImageToImageFilter}. These filters allow the standard allocation
structure to be used via {\em this$\rightarrow$AllocateOutputs()}. Explicit
allocation of device memory can be achieved using
{\em Image$\rightarrow$AllocateGPU()}
